### 2009-07-10 docs/architecture/architecture.tex
more arch stuff...

\subsection{`{\tt s}' and `{\tt u}' \multifab s (fluid state and velocity)}

The fluid state (density, enthalpy, species) are stored together in a
multi-component \multifab, typically named {\tt sold}, {\tt s1}, {\tt
s2}, or {\tt snew} (depending on which time-level it represents).

@@

In creating the advective fluxes, we need the velocity through the
faces of the zone---the $x$-velocity on the $x$-edges, the
$y$-velocity on the $y$-edges, etc (see figure~\ref{fig:mac}.  This
type of velocity discretization is termed the MAC velocity (after the
``marker-and-cell'' method for free boundaries in incompressible
flows, Harlow and Welch 1965).

@@

At each level of refinement, this is done by making a \multifab\
array where each of the {\tt dm} components is nodal in
its respective direction:
\begin{verbatim}
  type(multifab) :: umac(dm)

>>>>

\subsection{`{\tt s}' \multifab s (fluid state)}

The fluid state (density, enthalpy, species) are stored together in a
cell-centered multi-component \multifab, typically named {\tt sold},
{\tt s1}, {\tt s2}, or {\tt snew} (depending on which time-level it
represents).  The enthalpy is stored as $(\rho h)$, and the species
are stored as partial-densities $(\rho X_k)$.

Individual state variables should be indexed using the {\tt variables}
module, with {\tt rho\_comp} referring to the density, {\tt rhoh\_comp}
referring to the enthalpy quantity $(\rho h)$, and {\tt spec\_comp}
referring to the start of the species (partial densities).

To find a particular species, a query can be made through the {\tt network}
module, such as:
\begin{verbatim}
  ic12 = network_species_index("carbon-12")
\end{verbatim}
and then the \fab\ can be indexed using {\tt spec\_comp-1+ic12} to
get ``carbon-12''.

\subsection{`{\tt u}' \multifab s (fluid velocity)}

The fluid velocity at time-levels $n$ and $n+1$ is stored in
a cell-centered multi-component \multifab, typically named
{\tt uold} or {\tt unew}.  Here the {\tt dm}
components correspond to each coordinate direction.

@@

In creating the advective fluxes, we need the time-centered velocity
through the faces of the zone---the $x$-velocity on the $x$-edges, the
$y$-velocity on the $y$-edges, etc.\ (see figure~\ref{fig:mac}).  This
type of velocity discretization is termed the MAC velocity (after the
``marker-and-cell'' method for free boundaries in incompressible
flows, Harlow and Welch 1965).

@@

The MAC velocities are allocated at each level of refinement,{\tt n},
by making a \multifab\ array where each of the {\tt dm} components is
nodal in its respective direction:
\begin{verbatim}
  type(multifab) :: umac(dm)
